FinalManuscript_DISCS_UG

### 2019-03-06 parts/04_results.tex
\centering
Add table with images

% \begin{table*}
% 	\centering
% 	\caption{Comparison of intensity transformations under Paillier}
% 	\label{tbl:it-pal}
% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
% 		\hline
% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
% 		\hline
% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
% 		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
% 		\hline
% 	\end{tabular}
% \end{table*}
%
% \begin{table*}
% 	\centering
% 	\caption{Comparison of intensity transformations under DGK}
% 	\label{tbl:it-dgk}
% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
% 		\hline
% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
% 		\hline
% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
% 		(#2) & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
% 		\hline
% 	\end{tabular}
% \end{table*}

@@

\begin{table}[t]
	\caption{Logarithm transformation under DGK}
	\label{tbl:log-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
		\hline
    \end{tabular}
\end{table}

>>>>

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table*}

\begin{table*}
	\centering
	\caption{Comparison of intensity transformations under DGK}
	\label{tbl:it-dgk}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
		\hline
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
		\hline
		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
		(#2) & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
		\hline
	\end{tabular}
\end{table*}

@@

\begin{table}[t]
    \centering
	\caption{Logarithm transformation under DGK}
	\label{tbl:log-dgk}
    \begin{tabular}{lcccccc}
        \hline
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
		\hline
    \end{tabular}
\end{table}
